Spatial Coordination Of Stomatal Patterning Between Leaf Surfaces In Amphistomatous *Arabidopsis thaliana* Incurs No Photosynthetic Advantage

### 2023-09-27 ms/ms.Rmd
changed latex engine to xelatex

  It consists of two paragraphs.
keywords:
  - stomatal patterning
  - Aribidopsis thaliana
  - amphistomatous leaves
  - photosynthesis modeling
  - optimizing photosynthesis
  - CO$_2$ diffusion
fontsize: 12pt
#spacing: halfline # could also be oneline
#classoptions:
#  - endnotes
bibliography: stomata-spacing.bib
#csl: mycitationstyle.csl
link-citations: yes
output: rticles::oup_article
#urlcolor: orange
#linkcolor: green
#citecolor: red
header-includes:
 - \usepackage[nomarkers,tablesfirst]{endfloat} # For figures and tables at end
 - \usepackage{lineno} # For line numbering
 - \linenumbers # For line numbering
---

>>>>

  It consists of two paragraphs.
keywords:
  - stomatal patterning
  - Aribidopsis thaliana
  - amphistomatous leaves
  - photosynthesis modeling
  - optimizing photosynthesis
  - CO$_2$ diffusion
fontsize: 12pt
#spacing: halfline # could also be oneline
#classoptions:
#  - endnotes
bibliography: stomata-spacing.bib
#csl: mycitationstyle.csl
link-citations: yes
output: 
  rticles::oup_article:
    latex_engine: xelatex
#urlcolor: orange
#linkcolor: green
#citecolor: red
header-includes:
 - \usepackage[nomarkers,tablesfirst]{endfloat} # For figures and tables at end
 - \usepackage{lineno} # For line numbering
 - \linenumbers # For line numbering
---
